---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# im2pix

<!-- badges: start -->
[![R-CMD-check](https://github.com/TengMCing/im2pix/workflows/R-CMD-check/badge.svg)](https://github.com/TengMCing/im2pix/actions)
<!-- badges: end -->

im2pix is a tool to convert image to pseudo pixel art in R. It's a reduced version of [Nathan Harper's Python script](https://github.com/nathanharper/phixelgator). The author of this package do not own the copyright of this algorithm.  

## Installation

You can install the released version of im2pix from [GitHub](https://github.com/TengMCing/im2pix) with:

``` r
devtools::install_github("TengMCing/im2pix")
```

### For macOS users

This package heavily depends on the `imager` package. You may get an error like this when you run the `imtopix()` function or load the `imager` package on macOS. 

```r
Loading required package: imager
Error in dyn.load(file, DLLpath = DLLpath, ...) : 
  unable to load shared object '/Library/Frameworks/R.framework/Versions/3.3/Resources/library/imager/libs/imager.so':
  dlopen(/Library/Frameworks/R.framework/Versions/3.3/Resources/library/imager/libs/imager.so, 6): Library not loaded: /opt/X11/lib/libX11.6.dylib
  Referenced from: /Library/Frameworks/R.framework/Versions/3.3/Resources/library/imager/libs/imager.so
  Reason: image not found
```

This is because you are missing `X11` so you need to install/reinstall the latest version of `XQuartz` (https://www.xquartz.org/).

## Example

```{r example}
library(im2pix)
library(imager)
```



The built-in image

```{r cars}
plot(sample_im)
```

Covert the image to pseudo pixel art using palette "contra". Increase the block size will decrease the output resolution. 

The `imtopix()` function only accepts `cimg` class object/image which can be loaded from disk by `imager::load.image(<path_to_image>)` or created from a matrix-like object by `imager::as.cimg(<matrix-like_object>)`.


```{r}
out_pic <- imtopix(sample_im, pal = "contra", blockSize = 8)
plot(out_pic)
```

Using another palette 

```{r}
out_pic <- imtopix(sample_im, pal = "gameboy", blockSize = 8)
plot(out_pic)
```

Available palettes include

```{r}
names(pal_collection)
```

